%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page



% ------------------------ FONT TYPE ----------------------------
% character encoding
\usepackage[utf8]{helvet}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.77]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\firstname{Brian Aguirre}
\email{brian.n.aguirre@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{brianaguirre.github.io}                         % optional, remove / comment the line if not wanted
\extrainfo{@bnap48}                 % optional, remove / comment the line if not wanted

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

%------------------- EXPERIENCE -------------------
\section{Experience}

%\cventry
    %{year--year}
    %{Job title}
    %{Employer}
    %{City}{}
    %{Description}

\cventry
  {June 2017 - Present}
  {Software Developer on OSF Application}
  {Center for Open Science}
  {Charlottesville, Virginia}{}
  {Collaborator on the OSF Waterbutler and MFR applications. Improve comparability and readability for various research files. In charge of updating docs for Docker installation.}

\cventry
  {August 2016 - May 2017}
  {Computer Science Research Assistant}
  {University of Virginia, School of Engineering}
  {Charlottesville, Virginia}{}
  {Researched how AI and Machine Learning can help Open Source communities. Gathered data on GitHub repo's and created algorithms and tests that help determine how and why certain pull requests are accepted or denied.}

\cventry
  {Spring 2017}
  {Software Developer Extern}
  {Center for Open Science}
  {Charlottesville, Virginia}{}
  {Designer and developer of the new OSF dashboard site. Personalized content by building two new features -  “Recommended” and “History”, which automated searching through research projects and COS services. Winner of week long hackathon.}

\cventry
  {January 2015 - August 2016}
  {Computational Math Research Assistant}
  {University of Virginia, Department of Mathematics}
  {Charlottesville, Virginia}{}
  {Researched nxn matrix solving algorithms. Developed code to test compiler performance on various data structures. Traveled to many cities in the U.S. to present research.}

\cventry
  {August 2014 - January 2016}
  {IT Assistant}
  {Frank Batten School of Leadership \& Public Policy}
  {Charlottesville, Virginia}{}
  {Helped the staff, faculty, and students with various software and hardware issues. Built the frank batten community page, and created an encryption application to store sensitive student data.}

\cventry
  {October 2012 - May 2014}
  {Teaching Assistant }
  {Fairfax County Public Schools, AVID Program}
  {Falls Church, Virginia}{}
  {Teaching assistant for Calculus, Physics, and Chemistry courses at various high schools of FCPS. Helped students improve grades and prepapre for IB exams. }


%------------------- EDUCATION -------------------
\section{Education}
%\cventry {year--year} {Degree} {University of Virginia} {City} {\textit{Grade}} {Description}  % arguments 3 to 6 can be left empty

\cventry
  {August 2014 - May 2017}
  {B.A.}
  {University of Virginia}
  {Charlottesville, Virginia}
  {\textit{B.A. CS \& Mathematics, M.S. Mathematics Certificate}}
  {Four year undergraduate program that led to a graduate Math program. Studies primarily focused on computational mathematics, and software engineering. Course work included advanced programming, data structures, databases, DLD, HCI, AI, Linear Algebra, and Masters topology courses. \\\textit{Recipient of VMATYC \& COSYNE scholarships, Dean's List, and UVA's Who's Who Award, etc.}}


%------------------- COMPUTER SKILLS -------------------
\section{Skills}
\cvitem{Programming Languages}{JAVA, Python, C++, JavaScript, SQL}
\cvitem{Web Technologies}{HTML, CSS, Bootstrap, JQuery }
\cvitem{Systems \& Methodologies}{linux, git, DLD, testing (unit, xunit), Automation, HCI.}
\cvitem{Spoken Languages}{Fluent in English, Spanish, and French.}



\end{document}


%% end of file `template.tex'.
